sensi_an_rotations201911. To analyse rotation runs for paper

### 2019-11-22 inst/documents/sensi_an_rotations201911.Rmd
starting new plots for paper

    nruns_fail <- df_res_all %>% 
                  filter(gens_seq == max_gen & gens_rot == max_gen) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs not reaching thresholds : ', nruns_fail/nrow(df_res_all) )

    # remove runs where thresholds not reached for seq & rot 
    df_res_all <- df_res_all %>% 
                  filter(gens_seq != max_gen | gens_rot != max_gen)

    nruns_same <- df_res_all %>% 
                  filter(gens_seq == gens_rot) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs (that did reach threshold) where rotations and sequence the same  : ', nruns_same/nrow(df_res_all) )

    nruns_rot_20pc_better <- df_res_all %>% 
                  filter(rot_minus_seq/gens_seq >= 0.2 ) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs (that did reach threshold) where rotations >20 % better than sequence  : ', nruns_rot_20pc_better/nrow(df_res_all) )

# difference between rotations and sequences across all runs

    # print( ggplot(df_res_all, aes(x=rot_minus_seq)) + 
    #          
    #          geom_histogram(binwidth=10) +
    #          xlab('rot_minus_seq : rotation generations minus sequence') +
    #          ylab('count (sqrt scale to show low values)') +
    #          scale_y_sqrt(breaks=c(0,10,20,50,200,500,2000,5000)) + #can't use log scale because anchored at 0
    #          theme_minimal() +
    #          theme(panel.grid.minor.y=element_blank()))

# no colour ??
# ggplot(df_res_all, aes(x=rot_minus_seq, colour=rot_minus_seq)) + 
#      geom_histogram(binwidth=10) + 
#      scale_color_brewer(palette="Dark2")

@@

# plot all 160k runs together
# ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
#      geom_histogram(binwidth=widthbin, colour='white') + 
#      theme_minimal() +
#      theme(panel.grid.minor.y=element_blank())

#facet by A-D and 1-4
ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='white') + 
     theme_minimal() +
     xlim(-100,100) +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD))

# lengthening facet labels
idAD_lookup <- c(
  A = "A freq i-same",
  B = "B freq i-diff",
  C = "C mort i-same",
  D = "B mort i-diff"
)

id14_lookup <- c(
  "1" = "1 nocost nodisp",
  "2" = "2 costs nodisp",
  "3" = "3 nocost disp",
  "4" = "4 costs disp"
)

@@

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
#TODO make the best_strategy threshold basedon percent too
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("percentage advantage of rotations over sequence in generations") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

@@

@@

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    #plotlist[[plotnum]] <- 
    print( ggplot(df_res_all, aes_string(x=i, y=y)) +

@@

    x <- df_res_all[,in_cols]
    y <- df_res_all['rot_minus_seq']

@@

ggplot(df_res_all, aes(x=dom_sel, y=dom_cos)) + 
     geom_point(shape=3, size=1, alpha=0.2, show.legend=FALSE) +
     theme_minimal() +
     geom_point(data=filter(df_res_all, rot_minus_seq/gens_seq >= 0.3 ), shape=1, size=1, col='red', alpha=0.8)

# quick, not very successful look at modelling it
# library(mgcv)
# mod_lm2 <- gam(rot_minus_seq ~ cost + dom_cos + dom_sel, data=df_res_all)
# summary(mod_lm2)  
# 
# mod_gam2 <- gam(rot_minus_seq ~ s(cost) + s(dom_cos) + s(dom_sel) + s(rr) + s(expo_hi) + s(male_expo_prop) + s(eff) + s(start_freqs), data=df_res_all)
# 
# summary(mod_gam2)  
# #Deviance explained = 19.5%
# 
# mod_gam3 <- gam(rot_minus_seq ~ te(cost,dom_cos,dom_sel), data=df_res_all)
# summary(mod_gam3)

@@

    gg <- ggplot( df_res_all, aes_string(x='rot_interval',
                                         y='tot_gens_dep_under50',
                                         group='scenario',
                                         colour='scenario') ) +
          geom_line( alpha=0.5, lwd=1 )

@@

    gg <- ggplot( df_res_all, aes_string(x='eff',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_all, aes_string(x='expo_hi',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_all, aes_string(x='expo_hi*eff*male_expo_prop',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

>>>>

# difference between rotations and sequences, all runs

```{r fig-si-1-abs-diff-rot-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

# lengthening facet labels
# idAD_lookup <- c(
#   A = "A freq i-same",
#   B = "B freq i-diff",
#   C = "C mort i-same",
#   D = "B mort i-diff"
# )
# id14_lookup <- c(
#   "1" = "1 nocost nodisp",
#   "2" = "2 costs nodisp",
#   "3" = "3 nocost disp",
#   "4" = "4 costs disp"
# )

idAD_lookup <- c(
  A = "A frequency switch\n insecticides same",
  B = "B frequency switch\n insecticides different",
  C = "C mortality switch\n insecticides same",
  D = "D mortality switch\n insecticides different"
)

id14_lookup <- c(
  "1" = "1 no fit. costs\n no dispersal",
  "2" = "2 fit. costs\n no dispersal",
  "3" = "3 no fit. costs\n dispersal",
  "4" = "4 fit. costs and\n dispersal"
)

@@

# pcent difference between rotations and sequences, all runs

```{r fig1-pcent-diff-rot-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#rms (rot_minus_seq)_pcent, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=rms_percent, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     scale_x_continuous(limits=c(-80,80), breaks = c(-60,-40,-20,0,20,40,60)) +
     xlab("percentage advantage of rotations over sequence in generations") +
     theme(panel.grid.minor=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

# at each generations below threshold for rotations, which strategy was best

```{r fig2-which-best-each-gens-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

# at each generations below threshold for rotations, which strategy was best

```{r fig3-which-best-each-gens-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

    nruns_fail <- df_res_16 %>% 
                  filter(gens_seq == max_gen & gens_rot == max_gen) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs not reaching thresholds : ', nruns_fail/nrow(df_res_16) )

    # remove runs where thresholds not reached for seq & rot 
    df_res_16 <- df_res_16 %>% 
                  filter(gens_seq != max_gen | gens_rot != max_gen)

    nruns_same <- df_res_16 %>% 
                  filter(gens_seq == gens_rot) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs (that did reach threshold) where rotations and sequence the same  : ', nruns_same/nrow(df_res_16) )

    nruns_rot_20pc_better <- df_res_16 %>% 
                  filter(rot_minus_seq/gens_seq >= 0.2 ) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs (that did reach threshold) where rotations >20 % better than sequence  : ', nruns_rot_20pc_better/nrow(df_res_16) )

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    #plotlist[[plotnum]] <- 
    print( ggplot(df_res_16, aes_string(x=i, y=y)) +

@@

    x <- df_res_16[,in_cols]
    y <- df_res_16['rot_minus_seq']

@@

ggplot(df_res_16, aes(x=dom_sel, y=dom_cos)) + 
     geom_point(shape=3, size=1, alpha=0.2, show.legend=FALSE) +
     theme_minimal() +
     geom_point(data=filter(df_res_16, rot_minus_seq/gens_seq >= 0.3 ), shape=1, size=1, col='red', alpha=0.8)

@@

    gg <- ggplot( df_res_16, aes_string(x='rot_interval',
                                         y='tot_gens_dep_under50',
                                         group='scenario',
                                         colour='scenario') ) +
          geom_line( alpha=0.5, lwd=1 )

@@

    gg <- ggplot( df_res_16, aes_string(x='eff',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_16, aes_string(x='expo_hi',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_16, aes_string(x='expo_hi*eff*male_expo_prop',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)
